---
title: "demo"
author: "Sophie Paul"
date: '2022-06-01'
output: html_document
---

TODOs: generate hg38 bin annotations

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, eval=FALSE}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("QDNAseq")
BiocManager::install("QDNAseq.hg19")
```

```{r}
library(QDNAseq)
library(tidyverse)
```

## Setting bin size

Larger bin sizes recommended for shallow read depth: https://blog.goldenhelix.com/cnvcallerwholegenome/ (need to confirm)

Possible bin annotations:

- hg19.1kbp.SR50
- hg19.5kbp.SR50
- hg19.10kbp.SR50
- hg19.15kbp.SR50
- hg19.30kbp.SR50
- hg19.50kbp.SR50
- hg19.100kbp.SR50
- hg19.500kbp.SR50 
- hg19.1000kbp.SR50

PE supported but not included in package.

```{r}
# Using largest bin size supported
bins <- getBinAnnotations(binSize=1000)
```

# Data source

https://platform.dnanexus.com/panx/projects/GBFb6Qj4gK6P5jQ331vVP63g/data/

# sample A

### Read data

```{r, eval=FALSE}
readCounts <- binReadCounts(bins, path="test_data/") # legacy TSO500 data test
sample_a_readCounts <- binReadCounts(bins, path="~/workspace/investigations/qdnaseq/1-initial_testing/bams/pb/LP2103581-DNA_A01")

# haven't enough disk space to do both samples together
#save(sample_a_readCounts, file="LP2103581-DNA_A01.qdnaseq.Rdata")
```

```{r}
load("LP2103581-DNA_A01.qdnaseq.Rdata")
```

```{r}
noisePlot(sample_a_readCounts)
```

#### Filtering


```{r}
readCountsFiltered_a <- sample_a_readCounts %>%
    applyFilters(residual=TRUE, blacklist=100)
```

Isobar plot to visualise batch effects

- wonky because not WGS?

```{r}
isobarPlot(readCountsFiltered_a)
```

Calling pipeline:

```{r}
call_cnvs <- function(filtered_counts){
  filtered_counts %>%
    estimateCorrection() %>%
    correctBins() %>%
    normalizeBins() %>%
    smoothOutlierBins() %>%
    # sqrt means Anscombe transform; better than log2 at var stabilisation
    segmentBins(transformFun="sqrt") %>%
    normalizeSegmentedBins() %>%
    callBins()
}

copyNumbersCalled_a <- call_cnvs(readCountsFiltered_a)
```

```{r}
plot(copyNumbersCalled_a); highlightFilters()
```

Red: CGHBase probloss output
Blue: CGHBase probgain output

i.e.: `CGHBase::probloss(copyNumbersCalled_a)`

# sample B

```{r}
#sample_b_readCounts <- binReadCounts(bins, path = "~/workspace/investigations/qdnaseq/1-initial_testing/bams/LP2103059-DNA_A01")
#save(sample_b_readCounts, file = "LP2103059-DNA_A01.qdnaseq.Rdata")
```

```{r}
load("LP2103059-DNA_A01.qdnaseq.Rdata")
```

```{r}
readCountsFiltered_b <- sample_b_readCounts %>%
    applyFilters(residual=TRUE, blacklist=100)
```

```{r}
isobarPlot(readCountsFiltered_b)
```

```{r}
copyNumbersCalled_b <- call_cnvs(readCountsFiltered_b)
```

```{r}
plot(copyNumbersCalled_b)
highlightFilters()
```

```{r}
QDNAseq::noisePlot(copyNumbersCalled_b)
```

```{r}
png(filename = "test_data/%s")
plot(copyNumbersCalled)
dev.off()
```

```{r}
copyNumbersCalled@featureData@data %>%
  filter(chromosome == "7", start < 3000001) %>%
  ggplot() +
  geom_segment(aes(x = start, xend = end, y = gc, yend = gc))
```

```{r}
exportBins(copyNumbersCalled_a, format="seg", file = "%s")
copyNumbersCalled_b@assayData$segmented %>% data.frame() %>% `[`("9:1-1000000",)
```


