---
title: "Untitled"
author: "Sophie Paul"
date: '2022-06-30'
output: html_document
---

```{r}
library(QDNAseq)
library(tidyverse)
```

```{r}
paths <- list.files(
  path = "test_data/cnv_call_rds/", 
  pattern = ".RDS", 
  recursive = TRUE,
  full.names = TRUE
)

data_names <- str_replace(
  string = paths,
  pattern = ".+((?:git|qdna).+)/(.+)\\.(.+)\\.RDS", 
  replacement = "\\1.\\2.\\3"
)

cnv_calls <- map(
  .x = paths,
  .f = readRDS 
)

names(cnv_calls) <- data_names
```

# github_asntech.LP2103059-DNA_A01.100
# github_asntech.LP2103059-DNA_A01.1000
# github_asntech.LP2103059-DNA_A01.15
# github_asntech.LP2103059-DNA_A01.30
# github_asntech.LP2103059-DNA_A01.50
# github_asntech.LP2103059-DNA_A01.500
# github_asntech.LP2103581-DNA_A01.100
# github_asntech.LP2103581-DNA_A01.1000
# github_asntech.LP2103581-DNA_A01.15
# github_asntech.LP2103581-DNA_A01.30
# github_asntech.LP2103581-DNA_A01.50
# github_asntech.LP2103581-DNA_A01.500
# qdnaseq_dev.LP2103581-DNA_A01.100
# qdnaseq_dev.LP2103581-DNA_A01.1000
# qdnaseq_dev.LP2103581-DNA_A01.15
# qdnaseq_dev.LP2103581-DNA_A01.30

plot(cnv_calls[[1]])
plot(cnv_calls[[2]])
plot(cnv_calls[[3]])
plot(cnv_calls[[4]])
plot(cnv_calls[[5]])
plot(cnv_calls[[6]])
plot(cnv_calls[[7]])
plot(cnv_calls[[8]])
plot(cnv_calls[[9]])
plot(cnv_calls[[10]])
plot(cnv_calls[[11]])
plot(cnv_calls[[12]])
plot(cnv_calls[[13]])
plot(cnv_calls[[14]])
plot(cnv_calls[[15]])
plot(cnv_calls[[16]])



```{r}
plot(cnv_calls[[15]])
```


```{r}
cnv_calls["github_asntech.LP2103059-DNA_A01.50"]
QDNAseq::exportBins(cnv_calls[["github_asntech.LP2103059-DNA_A01.50"]], format = "seg", type = "calls", file = "%s.summarised_calls.tsv")
QDNAseq::exportBins(cnv_calls[["github_asntech.LP2103059-DNA_A01.50"]], format = "tsv", type = "calls", file = "LP2103059-DNA_A01.raw_calls_all_depths.tsv")
```

```{r}
QDNAseq::exportBins(cnv_calls[["github_asntech.LP2103581-DNA_A01.50"]], format = "seg", type = "calls", file = "%s.summarised_calls.tsv")
QDNAseq::exportBins(cnv_calls[["github_asntech.LP2103581-DNA_A01.50"]], format = "tsv", type = "calls", file = "LP2103581-DNA_A01.raw_calls_all_depths.tsv")
```

